\begin{thebibliography}{999}
	\bibitem{NFTGC} Even, Shimon; Tarjan, R. Endre (1975).
	"Network Flow and Testing Graph Connectivity".
    SIAM Journal on Computing
    \bibitem{DSNA} Tarjan, R. E. (1983).
    Data structures and network algorithms.
    \bibitem{MCIOI}胡伯涛 《最小割模型在信息学竞赛中的应用》
    \bibitem{ITA3}  Thomas H.Cormen / Charles E.Leiserson /
     Ronald L.Rivest / Clifford Stein.
     Introduction to Algorithms Third Edition
    \bibitem{kdTree}n+e 《K-D Tree 在信息学竞赛中的应用》
    \bibitem{huffman}M. J. Golin and G. Rote.
    A dynamic programming algorithm for constructing optimal
    prefix-free codes with unequal letter costs
    \bibitem{LLH}L. L. Larmore and D. S. Hirschberg.
    A fast algorithm for optimal length-limited Huffman codes
    \bibitem{chord} 陈丹琦《弦图与区间图》
    \bibitem{MMG}S. Micali and V. V. Vazirani,
    "An O($\sqrt{|v|}$|E|) algoithm for finding maximum matching
    in general graphs",
     21st Annual Symposium on Foundations of Computer Science (sfcs 1980)(SFCS),
     Syracuse, NY, USA USA, , pp. 17-27.
    doi:10.1109/SFCS.1980.12
    \bibitem{AGM} Anant Jindal and Gazal Kochar and Manjish Pal,
    "Maximum Matchings via Glauber Dynamics",CoRR
    \bibitem{GBT} Yang Zhe 《SPOJ375 QTREE解法的一些研究》
    \bibitem{BPSW} Robert Baillie; Samuel S. Wagstaff, Jr. (October 1980).
     "Lucas Pseudoprimes" (PDF). Mathematics of Computation. 35 (152):
      1391–1417.
    \bibitem{LAIA5}  David C. Lay , Steven R. Lay , Judi J. McDonald .
    Linear Algebra and Its Applications 5th Edition
\end{thebibliography}
